---
title: "Data Science and Statistics"
author: "Trever Yoder"
format: html
editor: visual
---

## Task 1: Answering Questions About Data Science

-   In a general sense, I think data science is about extracting information from data in order for it to be useful.
-   Differences
    -   Data scientists are typically focused on solving business problems while statisticians often focus on science
    -   Statisticians are more focused on modeling
        -   Statisticians bring data to models while data scientists bring models to their data
-   Similarities
    -   Both work with data and models
-   I view myself more as a data scientist than a statistician, but as I learn more about models and designing experiments, I feel more confident viewing myself as a statistician.

## Task 2: Running Code

Below is the R code to create an object called y:

```{r}
y <- density(iris$Petal.Width)
```

Now we will determine its class, type, and view a compact display of the structure of y:

```{r}
class(y)

typeof(y)

str(y)
```

Next, we will create a plot of y while hiding the code:

```{r}
#| echo: false
plot(y)
```

